%\fontsize{12pt}{13.2}\selectfont
\section{How to get help}

\frame{
\frametitle{How to start your project}
\begin{itemize}
\item Proposal for a small allocation
\item Develop and test your code
\item Run and evaluate scaling
\item Proposal for a medium (large) allocation
\end{itemize}
}

\subsection*{PDC suppport}
\frame{
\frametitle{PDC support}
\begin{itemize}
  
  \item Many questions can be answered by reading the web documentation: \alert{\url{https://www.pdc.kth.se/support}}
  \item Preferably contact PDC support by email: \alert{\url{support@pdc.kth.se}}
  \begin{itemize}
    \item you get a ticket number.
    \item always include the ticket number in follow-ups/replies\\ they look like this: [SNIC support \#12345]
  \end{itemize}
  \item Or by phone: \alert{$+46$ $(0)8$ $790$ $7800$}
  \item You can also make an appointment to \alert{come and visit}.
\end{itemize}
}


\subsection*{How to report problems}
\frame{
\frametitle{How to report problems \hfill  \alert{\url{support@pdc.kth.se}}}
\begin{itemize}
  \item Do not report new problems by replying to old/unrelated tickets.
  \item Split unrelated problems into separate email requests.
  \item Use a descriptive subject in your email.
  \item Give your PDC user name.
  \item Be as specific as possible.
  \item For problems with scripts/jobs, give an example.\\ Either send the example or make it accessible to PDC support.
  \item Make the problem example as small/short as possible.
  \item Provide all necessary information to reproduce the problem.
  \item If you want the PDC support to inspect some files, make sure that the files are readable.
  \item Do not assume that PDC support personnel have admin rights\\ to see all your files or change permissions.
\end{itemize}
}

\frame{\huge\centering Questions...?}